Zaca Fire Type Conversion

### 2020-09-17 Model Data Sheets and Code/Manuscript_Code.Rmd
minor changes
vsurf and model selection
Calculate RdNBR, import terrain and climate variables

@@

@@

@@

dem <- raster("E:/zaca/environmental_data/all_variables/dem_10m_zaca.tif")

vpd_jan <- raster("E:/zaca/environmental_data/cwd_vpd_amp/PRISM_vpdmax_30yr_normal_800mM2_01_asc/PRISM_vpdmax_30yr_normal_800mM2_01_asc.asc") %>% 
  projectRaster(., dem_30m) %>% 
  crop(., zaca) %>% 
  mask(., zaca)

#TPI
#Insolation
#Temp
#Rainfall

@@

#Run stepwise variable selection algorithm
mcf.vsurf <- VSURF(x = predictors, y = response)

>>>>

### Calculate NBR

#Directory will all pre-processed Landsat images
setwd("E:/zaca/type_conversion/Imagery/Level2")

for(img in list.files(path = ".", "GTiff$")){

  print(paste("Processing ", substr(img, 18, 25), sep = ""))

  #Merge bands into a brick
  image <- brick(img)

  NAvalue(image) <- -9999

  #Check sensor ID, mask using QA layer, and then compute NBR using appropriate formula
  if(as.numeric(substr(img, 3, 4)) == 8){

    print("Recognized Landsat 8")

    #Band designations change, depending on whether the OLI aerosol band is included
    if(nlayers(image) == 7){nbr <- (image[[5]] - image[[7]])/(image[[5]] + image[[7]])}
    else if(nlayers(image) == 6){nbr <- (image[[4]] - image[[6]])/(image[[4]] + image[[6]])}
    else {print("Incorrect number of bands")}

  } else if(as.numeric(substr(img, 3, 4)) == 5 | as.numeric(substr(img, 3, 4)) == 7) {

    print("Recognized Landsat 5 or 7")

    #Band 7 is the sixth band in the brick for TM/ETM
    if(nlayers(image) == 6){nbr <- (image[[4]] - image[[6]])/(image[[4]] + image[[6]])}
    else {print("Incorrect number of bands")}

    } else {print("Error recognizing sensor")}

  writeRaster(nbr, filename = paste("NBR_", substr(img, 18, 25), ".tif", sep = ""), format = "GTiff", NAflag = -9999)
  assign(paste("NBR_", substr(img, 18, 25)), nbr)

  rm(image, image_brick, nbr)

  print("Image completed")

}

### Calculate RdNBR

NBR_brick <- brick(NBR_2000, NBR_2001, NBR_2002, NBR_2003, NBR_2004, NBR_2005, NBR_2006, NBR_2007) * 1000

baseline_NBR <- calc(NBR_brick[[1:7]], fun = median)

RdNBR_2007 <- (baseline_NBR - NBR_brick[[8]]) / sqrt(abs(baseline_NBR/1000))

@@

#dem <- raster("E:/zaca/environmental_data/all_variables/dem_10m_zaca.tif")

@@

slope <- terrain(x = usgs_dem, opt = "slope", unit = "degrees", neighbors = 8)

aspect <- terrain(x = usgs_dem, opt = "aspect", unit = "degrees", neighbors = 8)

tpi <- terrain(x = usgs_dem, opt = "TPI") #Can calculate larger moving windows manually

@@

jan_max_vpd_30yr <- raster("E:/zaca/environmental_data/cwd_vpd_amp/PRISM_vpdmax_30yr_normal_800mM2_01_asc/PRISM_vpdmax_30yr_normal_800mM2_01_asc.asc") %>% 
  projectRaster(., template_30m, method = "ngb") %>% 
  crop(., zaca) %>% 
  mask(., zaca)

jan_min_temp_30yr <- raster("E:/zaca/type_conversion/Environmental_Variables/Climate/January_Min_Temperature/PRISM_tmin_30yr_normal_800mM2_01_asc/PRISM_tmin_30yr_normal_800mM2_01_asc.asc") %>% 
  projectRaster(., template_30m, method = "ngb") %>% 
  crop(., zaca) %>% 
  mask(., zaca)

aug_max_temp_30yr <- raster("E:/zaca/type_conversion/Environmental_Variables/Climate/August_Max_Temperature/PRISM_tmax_30yr_normal_800mM2_08_asc/PRISM_tmax_30yr_normal_800mM2_08_asc.asc") %>% 
  projectRaster(., template_30m, method = "ngb") %>% 
  crop(., zaca) %>% 
  mask(., zaca)

aug_max_vpd_30yr <- raster("E:/zaca/type_conversion/Environmental_Variables/Climate/August_Max_VPD/PRISM_vpdmax_30yr_normal_800mM2_08_asc/PRISM_vpdmax_30yr_normal_800mM2_08_asc.asc") %>% 
  projectRaster(., template_30m, method = "ngb") %>% 
  crop(., zaca) %>% 
  mask(., zaca)

annual_precip_30yr <- raster("E:/zaca/type_conversion/Environmental_Variables/Climate/Annual_Precipitation/PRISM_ppt_30yr_normal_800mM2_annual_asc/PRISM_ppt_30yr_normal_800mM2_annual_asc.asc") %>% 
  projectRaster(., template_30m, method = "ngb") %>% 
  crop(., zaca) %>% 
  mask(., zaca)

#Add Insolation

### Prepare Weather Data

jan_min_temp_2007 <- raster("E:/zaca/type_conversion/Environmental_Variables/Weather/January_Min_Temp/PRISM_tmin_stable_4kmM3_200701_bil/PRISM_tmin_stable_4kmM3_200701_bil.bil") %>% 
  projectRaster(., template_30m, method = "ngb") %>% 
  crop(., zaca) %>% 
  mask(., zaca)

aug_max_temp_2006 <- raster("E:/zaca/type_conversion/Environmental_Variables/Climate/August_Max_Temperature/PRISM_tmax_30yr_normal_800mM2_08_asc/PRISM_tmax_30yr_normal_800mM2_08_asc.asc") %>% 
  projectRaster(., template_30m, method = "ngb") %>% 
  crop(., zaca) %>% 
  mask(., zaca)

aug_max_vpd_2006 <- raster("E:/zaca/type_conversion/Environmental_Variables/Weather/August_Max_VPD/PRISM_vpdmax_stable_4kmM3_200608_bil/PRISM_vpdmax_stable_4kmM3_200608_bil.bil") %>% 
  projectRaster(., template_30m, method = "ngb") %>% 
  crop(., zaca) %>% 
  mask(., zaca)

annual_precip_30yr <- raster("E:/zaca/type_conversion/Environmental_Variables/Climate/Annual_Precipitation/PRISM_ppt_30yr_normal_800mM2_annual_asc/PRISM_ppt_30yr_normal_800mM2_annual_asc.asc") %>% 
  projectRaster(., template_30m, method = "ngb") %>% 
  crop(., zaca) %>% 
  mask(., zaca)

#Calculate precipitation for preceding year?

@@

#Run stepwise variable selection algorithm
mcf.vsurf <- VSURF(x = mcf.predictors, y = mcf.response)
